Exploring dimensions of biodiversity in Japanese ferns

### 2020-06-28 ms/manuscript.Rmd
Update plan
- add back in analysis of multiple k values for ecostructure
- track phylogeny file
- move categorize_endemism() to immediately after running ses analysis

```{r plot-prep}
tax_regions_data <- regions_taxonomy %>%
  mutate(taxonomic_cluster = as.factor(cluster) %>% fct_infreq %>% as.numeric %>% as.factor)

phy_regions_data <- regions_phylogeny %>%
  mutate(phylo_cluster = as.factor(cluster) %>% fct_infreq %>% as.numeric %>% as.factor)

ses_div_ferns_spatial <-
  shape_ferns %>%
  left_join(categorize_endemism(ses_phy_ferns), by = c(grids = "site")) %>%
  left_join(ses_traits_ferns, by = c(grids = "site")) %>%
  mutate(redundancy = 1 - (richness/abundance)) %>%
  left_join(tax_regions_data, by = "grids") %>%
  left_join(phy_regions_data, by = "grids")

ses_div_ferns_endemic_spatial <-
shape_ferns %>%
  left_join(categorize_endemism(ses_phy_ferns_endemic), by = c(grids = "site"))

@@

>>>>

```{r plot-prep}
tax_regions_data <- regions_taxonomy %>%
  mutate(taxonomic_cluster = as.factor(cluster) %>% fct_infreq %>% as.numeric %>% as.factor) %>%
  select(grids, taxonomic_cluster)

phy_regions_data <- regions_phylogeny %>%
  mutate(phylo_cluster = as.factor(cluster) %>% fct_infreq %>% as.numeric %>% as.factor) %>%
  select(grids, phylo_cluster)

ses_div_ferns_spatial <-
  shape_ferns %>%
  left_join(ses_phy_ferns, by = c(grids = "site")) %>%
  left_join(ses_traits_ferns, by = c(grids = "site")) %>%
  left_join(tax_regions_data, by = "grids") %>%
  left_join(phy_regions_data, by = "grids")

ses_div_ferns_endemic_spatial <-
shape_ferns %>%
  left_join(ses_phy_ferns_endemic, by = c(grids = "site"))

@@

```{r diversity-by-cluster}
ses_div_ferns_spatial %>%
  filter(taxonomic_cluster %in% c(1,2,3,4)) %>%
  as_tibble %>%
  select(mpd_obs_z, mpd_morph_obs_z, pe_obs_z, taxonomic_cluster) %>%
  pivot_longer(names_to = "var", values_to = "value", -taxonomic_cluster) %>%
  ggplot(aes(x = taxonomic_cluster, y = value)) +
  geom_jitter() +
  geom_boxplot(color = "grey80", fill = "transparent", outlier.shape = NA, alpha = 0.5) +
  facet_wrap(vars(var)) +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_blank(),
  )
```

Standard effect size (SES) of mean phylogenetic distance (MPD), mean morphological distance (MMD), and phylogenetic endemism (PE) by taxonomic bioregion (top four regions with the most sites only shown).
